\documentclass[common.tex]{subfiles}

\begin{document}
\makecvtitle

% \cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

\section{Education}
\cventry{2007--2008}{IGCSE}{International School of Hout Bay}{}{International Certificate of Education with Distinction}{%
%    Highest mark in South Africa for Mathematics\\
%    Highest mark in South Africa for Physics\\
%    Highest mark in South Africa for Information Technology
}
\cventryfollowon{2009--2010}{International Baccalaureate}{}{}{35 points}{%
%    Highest Achievement in Mathematics\\
%    Highest Achievement in Physics
}
\vspace{3pt}
\cventry{2011--2014}{B.Sc.~Mathematics and Computer Science}{University of Cape Town}{}{}{%
    Dean's merit list
}
\cventryfollowon{2016 (expected)}{B.Sc.~(Hons.) Computer Science}{}{}{}{%
    Thesis topic: test-driven development for ontology engineering
}

\section{Work Experience}
\cventry{Dec 2010--Feb 2011}{Science processing intern}{SKA Africa}{Cape Town}{}{
  Analysed data from the KAT7 radio telescope to search for unusual phenomena.
}
\cventry{Jul 2011}{Software developer intern}{Praekelt Foundation}{Cape Town}{}{
  Implemented a Bayesian filter for user content, to be integrated with mobile web portal \emph{Young Africa Live}.
}
\cventry{Sep 2011}{Software developer intern}{RightShift}{Cape Town}{}{
  Optimised the stochastic behaviour of online casino games.
}
\cventry{Dec 2011--Feb 2012}{Software developer intern}{Teach Me 2}{Cape Town}{}{
  Developed a stand-alone web application offering templated PDF generation.
}
\cventry{Jun 2012--Jul 2012}{Software developer intern}{Krit}{Cape Town}{}{
  Developed utilities for keyword extraction from user-written reviews.
}
\cventry{Dec 2012--Feb 2013}{Software engineer intern}{Facebook}{Menlo Park, California}{}{
  Developed internal tools for Hadoop Distibuted File System.
}
\cventry{Jun 2014--Jul 2014}{Software developer intern}{Oracle}{Cape Town}{}{
  Developed a Vagrant plugin to use Oracle Cloud as a virtualization provider.
}
\cventry{Jun 2013--Jul 2013}{Software development engineer intern}{Amazon}{Cape Town}{}{
  Integrated internal tools into a web frontend.
}
\cventryfollowon{Nov 2013--Feb 2014}{Software development engineer intern}{}{}{}{
  Developed a framework and automated service for metric aggregation and reporting.
}
\cventryfollowon{Nov 2014--Aug 2015}{Software development engineer intern}{}{}{}{
  Developed and maintained numerous internal operational tools.
}
\cventry{Oct 2015--Jan 2016}{Data science intern}{Jumo}{}{}{
  Assisted with infrastructure and data storage.  Designed and developed internal microservices and APIs.
}

\clearpage

\section{Achievements}
\cventry{2005}{South African team}{Primary Mathematics World Contest}{Hong Kong}{}{}
\cventry{2006--2010}{Gold award}{UCT Mathematics Olympiad}{}{}{}
\cventry{2006--2009}{Western Cape team}{Interprovincial Mathematics Olympiad}{}{}{}
\cventry{2007--2010}{Finalist}{South African Mathematics Olympiad}{}{}{}
\cventry{2006}{Silver medal}{Eskom Science Expo}{}{}{}
\cventryfollowon{2008}{Gold medal}{Eskom Science Expo}{}{}{}
\cventry{2009}{Finalist}{South African Computer Olympiad}{}{}{}
\cventryfollowon{2010}{Silver medal}{South African Computer Olympiad}{}{}{}
\cventry{2011}{South African team}{International Olympiad in Informatics}{Pattaya, Thailand}{}{}
\cventry{2014}{World finalist}{ACM International Collegiate Programming Contest}{Yekaterinburg, Russia}{}{}

\section{Community Involvement}
\cventry{2009--2013}{Deputy chair, volunteer lecturer}{UCT Algorithm Circle}{}{}{Student society aimed at spreading interest and knowledge of advanced computer science, with weekly classes on various topics.}
\cventry{2012}{Committee member, administrator}{The Shuttleworth Lab}{}{}{}
\cventry{2011--2013}{Volunteer}{Umonya}{}{}{Non-profit organisation which hosts free courses on Python programming for high school students.}
\cventry{2011--2012}{Scientific committee}{South African Computer Olympiad}{}{}{Setting problems and managing all technical aspects of the contest.}
\cventry{2012}{Deputy team leader}{International Olympiad in Informatics}{Montichiari, Italy}{}{}

\end{document}
